Exploratory Analysis Script

### 2024-03-28 code/eda-code/eda.qmd
Updated the predictor variable rds file error
Updated the summary table for our predictor variables

# Converting region from factor to numeric
selected_variables$region <- as.numeric(as.factor(selected_variables$region))

# Asia = 1
# Africa = 2
# Europe = 3
# Latin America & the Caribbean = 4
# Oceania = 5

@@

# Save to file 
summarytable_file <- here("results", "tables", "predictortable.rds")
saveRDS(predictor_table, file = summarytable_file)
```

>>>>

selected_variables <- selected_variables %>% 
  arrange(region)

@@

# Save to file 
summarytable_file <- here("results", "tables", "predictortable.rds")
saveRDS(predictortable, file = summarytable_file)
```
